Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-06 WRITEUP/ms.tex
refined Sec 6

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss_16_toomre_proj_1}
\caption{Continued. Maps showing the various quantities projected in the $xz$-plane.}
\addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss_16_toomre_proj_2}
\caption{Continued. Maps show the various quantities projected in the $yz$-plane.}
\end{figure*}

@@

We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to
those observed in $z$\ssim2 starburst galaxies.
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds.
The more massive and bigger MCs in \flower compared to the Milky Way
likely result from the higher gas mass fraction, surface density, and velocity dispersion,
which set the scale for fragmentation.
This is consistent with what has been found previously in higher resolution idealized simulation of isolated galaxies.
Our simulation here confirms these results at EoR and under
the influence of continuous gas accretion from the surrounding IGM (see e.g., \citealt{Klessen10a, Goldbaum11a}).

We compare the dynamics of MCs in \flower to \obs in the context of the Larson's relation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the 
density threshold $n_{\rm cut}$ adopted in identifying the structures.
Our results are thus insensitive to the various density cuts of choice.
%However, our results are dependent on the numerical resolution of the simulation.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the 
density threshold and even for the molecular substructures.
Such a high velocity dispersion likely results from
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.

@@

Determining the multi-phase ISM properties of early galaxies
is a critical piece to understanding the evolution and
assembly history of galaxies, since they set the pace
for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
Observations leveraging the combination of spatial-spectral imaging of
multi-band continuum and spectral line emission are crucial for better understanding
the role of \highz galaxy populations
in the context of galaxy evolution and the ISM physics behind their intense star formation in the early Universe.
Cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
statistics and is subject to the sub-grid models adopted, 
serve as an useful avenue/tool for examining and making predictions on the morphology and dynamics of
the multi-phase ISM structures of the first galaxies.
These predictions can in turn be
tested with high resolution imaging of the gas content in the first galaxies with telescopes such as ALMA and the ngVLA,
enabling us to test our findings and refine future simulations to shed light on the physical processes behind 
\SF since the cosmic dark ages.

@@

We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data.
T.K.D.L. acknowledges support by the NSF through award SOSPA4-009
from the NRAO and support from the Simons Foundation.
A.F. acknowledges support from the ERC Advanced Grant INTERSTELLAR H2020/740120.
This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA)
held at the Center for
Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli
Foundation and the Simons Foundation.
We thank the KSPA Scientific and Local Organizing Committees, and the program founder,
Pascale Garaud, for supporting the genesis of this work.
We also thank the Center for Cosmology and Particle Physics
at the New York University
for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
This research has made use of NASA's Astrophysics Data System Bibliographic Services
and \ncode{yt}, a community-developed Python package for analyzing simulation data in Astronomy.

>>>>

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss_16_toomre_proj_1}
\caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
\addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss_16_toomre_proj_2}
\caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
\end{figure*}

@@

We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to
those observed in $z$\ssim2 starburst galaxies.
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds.
The more massive and bigger MCs in \flower compared to the Milky Way
likely result from the higher gas mass fraction, surface density, and velocity dispersion,
which set the scale for fragmentation.
This physical scale is 
consistent with what has been found in higher resolution idealized simulation of isolated galaxies.
Our simulation here confirms these results at EoR and under
the influence of continuous gas accretion from the surrounding IGM (see e.g., \citealt{Klessen10a, Goldbaum11a}).

We compare the dynamics of MCs in \flower to \obs in the context of the Larson's relation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the 
density threshold $n_{\rm cut}$ adopted in identifying the structures.
Our results are thus insensitive to the various density cuts of choice.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the 
density threshold and even for the molecular substructures.
Such a high velocity dispersion likely results from
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.

@@

Determining the multi-phase ISM properties of early galaxies
is a critical piece to understanding the evolution and
assembly history of galaxies, since they set the pace
for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
Observations leveraging the combination of spatial-spectral imaging of
multi-band continuum and spectral line emission are crucial for better understanding
the role of \highz galaxy populations
in the context of galaxy evolution and the ISM physics behind their intense star formation in the early Universe.
Cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
statistics and is subject to the sub-grid models adopted, 
serve as an useful avenue/tool for examining and making predictions on the morphology and dynamics of
the multi-phase ISM of the first galaxies.
%Future higher resolution zoom-in simulations would certainly be useful to understand
%the evolving dynamical properties of the lower-mass molecular structures in
%galaxies at EoR under the influence of gas inflow/outflow (i.e., accounting for energy injection at large scale due to infall/outflow).
These predictions can in turn be
tested with high resolution imaging of the gas content in the first galaxies with telescopes such as ALMA and the ngVLA, thereby 
enabling us to test our findings and refine future simulations to shed light on the physical processes behind 
\SF since the cosmic dark ages.

@@

We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data.
TKDL acknowledges support by the NSF through award SOSPA4-009
from the NRAO and support from the Simons Foundation.
AF acknowledges support from the ERC Advanced Grant INTERSTELLAR H2020/740120.
This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA)
held at the Center for
Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli
Foundation and the Simons Foundation.
We thank the KSPA Scientific and Local Organizing Committees, and the program founder,
Pascale Garaud, for supporting the genesis of this work.
We also thank the Center for Cosmology and Particle Physics
at the New York University
for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
This research has made use of NASA's Astrophysics Data System Bibliographic Services
and \ncode{yt}, a community-developed Python package for analyzing simulation data in Astronomy.
